Can greedy-like heuristics be useful for solving the Weighted Orthogonal Art Gallery Problem under regular grid discretization?

### 2020-10-10 doc/paper.tex
update

 We used two different kind of benchmark sets:
     \begin{itemize}
     	 \item \emph{MinArea} instances:\fxnote{TODO:Milan: main characteristics, why they differ from others}
     	 \item \emph{FAT} instances: \fxnote{TODO: Milan: main characteristics, why they differ from others}
     \end{itemize}
     For \emph{MinArea} and \emph{FAT} instances, one polygon for each $n \in\{8,10,...,200\}$ has been generated, which makes 96 instances per each benchmark set. In overall, we have 192 polygons. 
	We included two kind of weights into each of (192) polygons:
	\begin{itemize}
		\item \emph{topologically-based related weights}. For each vertex $i$ of polygon $P$ let us denote by $l_i$ and $l_{i+1}$ the lengths of edges that comes out of vertex $i$. Then, $w_i := \frac{l_i + l_{i+1}}{2}$. This way of assigning weights is augmented by the fact that if the the arithmetic length of both edges that comes out of vertex $i$ is longer, it is expected that vertex is a guard can see a larger pieces of polygon $P$. This implies that the range of camera $i$ has to be larger, which again means that it has a higher price. In case of the second smaller edge, we add the arithmetic mean for the both lengths as a price of the vertex.
		\item \emph{point-based related weights:} For each vertex $j$, we consider the number of points in $D(P)$ that are visible from the given vertex $(|V(j)|)$. Based on this number, we assign prices to the vertices on the following way:
		\begin{equation}
		w_j = n \cdot \frac{|V(j)|}{|D(P)|}, j=1,...,n.
		\end{equation}
	\end{itemize}

     \subsection{Settings and the choice of the Parameters}
      All variants of our algorithms were implemented in C++ with g++~7.4 and the experiments were conducted in single-threaded mode on a machine with an Intel Xeon E5-2640 processor with 2.40 GHz and a memory limit of 8GB. The maximum computation time of each of our algorithms was set to 5 min.

@@

     \begin{table}[]
     	\centering
     	 \scalebox{0.85}{
     	\begin{tabular}{l|lllllll} \hline
     		Alg.           & $\bar{|s|}$ & $\bar{t}[s]$ &   $\bar{|g|}$ &optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
     		\textsc{Cplex}            & 15.93  & 0.15    & 18.93     & 97/97     & 0.00    & N/A        & N/A      \\
     		\textsc{Cp}               & 16.04  & 98.22   & 18.96     & 67/97     & 0.02    & N/A        & N/A      \\
     		\textsc{Greedy-1}             & 22.63  & 0.00    & 26.28     & 0/97      & 0.79    & 3/97       & 7.61     \\
     		\textsc{Greedy-2}          & 19.97  & 0.00    & 20.14     & 0/97      & 0.44    & 0/97       & 0.20     \\
     		   \textsc{Greedy-1+Cplex}  & 18.49  & 0.07    & 21.19     & 2/97      & 0.30    & 57/97      & 0.06     \\
     		   \textsc{Greedy-2+Cplex} & 18.39  & 0.00    & 19.59     & 0/97      & 0.26    & 53/97      & 0.04  \\ \hline 
     	\end{tabular}}
     \end{table}

      \begin{table}[]
      	\centering
      	\scalebox{0.85}{
      	\begin{tabular}{l|lllllll} \hline
      		Alg.           & $\bar{|s|}$ & $\bar{t}[s]$ &  $ \bar{|g|}$ &optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
      		\textsc{Cplex}            & 36.03  & 0.00    & 18.93     & 97/97     & 0.00    & N/A        & N/A      \\
      		\textsc{Cp}               & 36.03  & 18.95   & 18.93     & 97/97     & 0.00    & N/A        & N/A      \\
      		\textsc{Greedy-1}             & 39.28  & 0.00    & 20.15     & 2/97      & 0.35    & 4/97       & 0.24     \\
      		\textsc{Greedy-2}          & 40.92  & 0.00    & 20.96     & 0/97      & 0.51    & 0/97       & 0.40     \\
      		   \textsc{Greedy-1+Cplex}  & 37.78  & 0.01    & 19.41     & 4/97      & 0.21    & 19/97      & 0.08     \\
      		   \textsc{Greedy-2+Cplex} & 37.31  & 0.00    & 19.58     & 2/97      & 0.15    & 81/97      & 0.19   \\ \hline  
      	\end{tabular}}
      \end{table}

     \begin{table}[]
      \centering
       \scalebox{0.85}{
     	\begin{tabular}{l|lllllll} \hline
     		Alg.           & $\bar{|s|}$ & $\bar{t}[s]$ &   $\bar{|g|}$ &optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
     		\textsc{Cplex}            & 2.62   & 0.02    & 7.32      & 97/97     & 0.00    & N/A        & N/A      \\
     		\textsc{Cp}               & 2.62   & 8.17    & 7.32      & 97/97     & 0.00    & N/A        & N/A      \\
     		\textsc{Greedy-1}             & 3.39   & 0.35    & 7.81      & 0/97      & 0.09    & 23/97      & 0.05     \\
     		\textsc{Greedy-2}          & 3.52   & 0.32    & 6.61      & 2/97      & 0.10    & 28/97      & 0.08     \\
     		   \textsc{Greedy-1+Cplex}  & 3.34   & 0.35    & 8.91      & 4/97      & 0.08    & 25/97      & 0.04     \\
     		   \textsc{Greedy-2+Cplex} & 3.32   & 0.33    & 6.81      & 6/97      & 0.08    & 25/97      & 0.04  \\ \hline   
     	\end{tabular}}
     \end{table}

    \begin{table}[]
    	\centering
    	\scalebox{0.85}{
 	  \begin{tabular}{l|lllllll} \hline
 		Alg.           & $\bar{|s|}$ & $\bar{t}[s]$ &   $\bar{|g|}$ & optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
 		\textsc{Cplex}            & 6.72   & 0.02    & 6.44      & 97/97     & 0.00    & N/A        & N/A      \\
 		\textsc{Cp}               & 6.72   & 0.36    & 6.44      & 97/97     & 0.00    & N/A        & N/A      \\
 		\textsc{Greedy-1}             & 6.77   & 0.31    & 6.49      & 92/97     & 0.02    & 92/97      & 0.04     \\
 		\textsc{Greedy-2}          & 6.77   & 0.31    & 6.49      & 92/97     & 0.02    & 92/97      & 0.04     \\
 		   \textsc{Greedy-1+Cplex}  & 6.73   & 0.32    & 6.45      & 96/97     & 0.01    & 96/97      & 0.03     \\
 		   \textsc{Greedy-2+Cplex} & 7.42   & 0.31    & 6.46      & 90/97     & 0.33    & 92/97      & 0.33    \\ \hline
 	\end{tabular}}
   \end{table}

>>>>

 We used two different kind of benchmark sets:
     \begin{itemize}
     	 \item \emph{MinArea} instances:\fxnote{TODO:Milan: main characteristics, why they differ from others}
     	 \item \emph{FAT} instances: \fxnote{TODO: Milan: main characteristics, why they differ from others}
     \end{itemize}
     For \emph{MinArea} and \emph{FAT} instances, one polygon for each $n \in\{8,10,...,200\}$ has been generated, which makes 97 instances per each benchmark set. In overall, we have 194 polygons. 
	We included two kind of weights into each of (194) polygons:
	\begin{itemize}
		\item \emph{topologically-based related weights} ($W0$): For each vertex $v_i$ of polygon $P$ we denote by $l_i$ and $l_{i+1}$ the lengths of two edges that come out of the vertex $v_i$. Then, we set $w_i := \frac{l_i + l_{i+1}}{2}$. This way of assigning weights is augmented by the fact that if the the arithmetic length of both edges that comes out of vertex $i$ is longer, it is expected that a guard can see a larger pieces of polygon $P$. This implies that the spectrum of camera installed at $v_i$ has to be larger, which implies that it should be of a higher quality, i.e,. a higher price. In case that we have the second edge begin smaller, we consider arithmetic mean of the both lengths as the weight of the vertex.
		\item \emph{point-based related weights} ($W1$): For each vertex $j$, we consider the number of points in $D(P)$ that are visible from the given vertex $(|V(j)|)$. Based on this, we assign prices to each vertex on the following way:
		\begin{equation}
		w_i = n \cdot \frac{|V(i)|}{|D(P)|}, i=1,...,n.
		\end{equation}
	\end{itemize}

     \subsection{Settings and the choice of the Parameters}
      All variants of our algorithms were implemented in C++ with g++~7.4 and the experiments were conducted in single-threaded mode on a machine with an Intel Xeon E5-2640 processor with 2.40 GHz and a memory limit of 8GB. The maximum computation time of each of our algorithms was set to $5\ min$.

@@

     \begin{table}[]
     	\centering
     	 \scalebox{0.85}{
     	\begin{tabular}{l|lllllll}    \hline
     		Alg.           & $\bar{|s|}$ & $\bar{t}[s]$ &   $\bar{|g|}$ &optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
     		\textsc{Cplex}            & 15.93  & 0.15    & 18.93     & 97/97     & 0.00    & N/A        & N/A      \\
     		\textsc{Cp}               & 16.04  & 98.22   & 18.96     & 67/97     & 0.02    & N/A        & N/A      \\
     		\textsc{Greedy-1}             & 22.63  & 0.00    & 26.28     & 0/97      & 0.79    & 3/97       & 7.61     \\
     		\textsc{Greedy-2}          & 19.97  & 0.00    & 20.14     & 0/97      & 0.44    & 0/97       & 0.20     \\
     		   \textsc{Greedy-1+Cplex}  & 18.49  & 0.07    & 21.19     & 2/97      & 0.30    & 57/97      & 0.06     \\
     		   \textsc{Greedy-2+Cplex} & 18.39  & 0.00    & 19.59     & 0/97      & 0.26    & 53/97      & 0.04  \\ \hline 
     	\end{tabular}}
        \caption{The results on the benchmark set $MinArea$ for the type of weight $W0$.}
     \end{table}

      \begin{table}[]
      	\centering
      	\scalebox{0.85}{
      	\begin{tabular}{l|lllllll} \hline
      		Alg.           & $\bar{|s|}$ & $\bar{t}[s]$ &  $ \bar{|g|}$ &optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
      		\textsc{Cplex}            & 36.03  & 0.00    & 18.93     & 97/97     & 0.00    & N/A        & N/A      \\
      		\textsc{Cp}               & 36.03  & 18.95   & 18.93     & 97/97     & 0.00    & N/A        & N/A      \\
      		\textsc{Greedy-1}             & 39.28  & 0.00    & 20.15     & 2/97      & 0.35    & 4/97       & 0.24     \\
      		\textsc{Greedy-2}          & 40.92  & 0.00    & 20.96     & 0/97      & 0.51    & 0/97       & 0.40     \\
      		   \textsc{Greedy-1+Cplex}  & 37.78  & 0.01    & 19.41     & 4/97      & 0.21    & 19/97      & 0.08     \\
      		   \textsc{Greedy-2+Cplex} & 37.31  & 0.00    & 19.58     & 2/97      & 0.15    & 81/97      & 0.19   \\ \hline  
      	\end{tabular}}
         \caption{The results on the bemchmark set $MinArea$ for the  type of weight $W1$.}
      \end{table}

     \begin{table}[]
      \centering
       \scalebox{0.85}{
     	\begin{tabular}{l|lllllll} \hline
     		Alg.           & $\bar{|s|}$ & $\bar{t}[s]$ &   $\bar{|g|}$ &optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
     		\textsc{Cplex}            & 2.62   & 0.02    & 7.32      & 97/97     & 0.00    & N/A        & N/A      \\
     		\textsc{Cp}               & 2.62   & 8.17    & 7.32      & 97/97     & 0.00    & N/A        & N/A      \\
     		\textsc{Greedy-1}             & 3.39   & 0.35    & 7.81      & 0/97      & 0.09    & 23/97      & 0.05     \\
     		\textsc{Greedy-2}          & 3.52   & 0.32    & 6.61      & 2/97      & 0.10    & 28/97      & 0.08     \\
     		   \textsc{Greedy-1+Cplex}  & 3.34   & 0.35    & 8.91      & 4/97      & 0.08    & 25/97      & 0.04     \\
     		   \textsc{Greedy-2+Cplex} & 3.32   & 0.33    & 6.81      & 6/97      & 0.08    & 25/97      & 0.04  \\ \hline   
     	\end{tabular}}
          \caption{The results on the benchmark set $FAT$ for the type of weight $W0$.}
     \end{table}

    \begin{table}[]
    	\centering
    	\scalebox{0.85}{
 	  \begin{tabular}{l|lllllll} \hline
 		Alg.           & $\bar{|s|}$ & $\bar{t}[s]$ &   $\bar{|g|}$ & optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
 		\textsc{Cplex}            & 6.72   & 0.02    & 6.44      & 97/97     & 0.00    & N/A        & N/A      \\
 		\textsc{Cp}               & 6.72   & 0.36    & 6.44      & 97/97     & 0.00    & N/A        & N/A      \\
 		\textsc{Greedy-1}             & 6.77   & 0.31    & 6.49      & 92/97     & 0.02    & 92/97      & 0.04     \\
 		\textsc{Greedy-2}          & 6.77   & 0.31    & 6.49      & 92/97     & 0.02    & 92/97      & 0.04     \\
 		   \textsc{Greedy-1+Cplex}  & 6.73   & 0.32    & 6.45      & 96/97     & 0.01    & 96/97      & 0.03     \\
 		   \textsc{Greedy-2+Cplex} & 7.42   & 0.31    & 6.46      & 90/97     & 0.33    & 92/97      & 0.33    \\ \hline
 	\end{tabular}}
    \caption{The results on the benchmark set $FAT$ for the type of weight $W1$.}
   \end{table}
